---
title: "Plastic"
author: "Yun He, Jun Lu, Chu Yu, Chunxiao Zhai, Haoran Hu"
date: "11/21/2018"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(SASxport)
knitr::opts_chunk$set(
    fig.align = 'center',
    fig.width = 7,
    fig.asp = 0.6,
    out.width = "80%",
    message = F,
    warning = F
 )
theme_set(theme_bw() + theme(legend.position = "bottom"))


```

## Overview

## Data sources
All data was retrieved from the the [National Health and Nutrition Examination Survey](https://www.cdc.gov/nchs/nhanes/index.htm). 

We download demographics data ([DEMO2011-2012][1], [DEMO2013-2014][2] and [DEMO2015-2016][3]), phthalates metabolites data ([PHTHTE2011-2012][4], [PHTHTE2013-2014][5] and [PHTHTE2015-2016][6]) and body measures data ([BMX2011-2012][7], [BMX2013-2014][8] and [BMX2015-2016][9]) into three local files.

[1]:https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/DEMO_G.XPT
[2]:https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/DEMO_H.XPT
[3]:https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/DEMO_I.XPT
[4]:https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/PHTHTE_G.XPT
[5]:https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/PHTHTE_H.XPT
[6]:https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/PHTHTE_I.XPT
[7]:https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/BMX_G.XPT
[8]:https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/BMX_H.XPT
[9]:https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/BMX_I.XPT


1. Variables used in demographics data:

* `SEQN `: Respondent sequence number
* `RIAGENDR`: Gender
* `RIDAGEYR`: Age
* `RIDRETH3`: Race and Hispanic origin information, with Non-Hispanic Asian Category
* `INDFMPIR`: Ratio of family income to poverty

2. Variables used in phthalates metabolites data:

* `SEQN `: Respondent sequence number
* `URXMEP`: Mono-ethyl phthalate (ng/mL)
* `URXMBP`: Mono-n-butyl phthalate (ng/mL)
* `URXMIB`: Mono-isobutyl phthalate (ng/mL)
* `URXMC1`: Mono-(3-carboxypropyl) phthalate (ng/mL)
* `URXMZP`: Mono-benzyl phthalate (ng/mL)
* `URXMHP`: Mono-(2-ethyl)-hexyl phthalate (ng/mL)
* `URXMHH`: Mono-(2-ethyl-5-hydroxyhexyl) phthalate (ng/mL)
* `URXMOH`: Mono-(2-ethyl-5-oxohexyl) phthalate (ng/mL)

3. Variables used in phthalates metabolites data

* `SEQN `: Respondent sequence number
* `BMXBMI`: Body Mass Index (kg/m**2)
* `BMDBMIC`: BMI Category - Children/Youth

## Get the data
```{r}
download_nhanes = function(year, data_category){
  letter = c("2011-2012" = "G", "2013-2014" = "H", "2015-2016" = "I")
  url = str_c("https://wwwn.cdc.gov/Nchs/Nhanes/", year, "/", data_category, "_", letter[year], ".XPT")
  destfile_name = str_c("./data/", data_category, "/", data_category, year, ".XPT")
  download.file(url, destfile = destfile_name, method = "curl")
}


if (!file.exists("data")) {
  dir.create("./data")
  dir.create("./data/DEMO")
  dir.create("./data/PHTHTE")
  dir.create("./data/BMX")
  year = c("2011-2012", "2013-2014", "2015-2016")
  map(year, ~download_nhanes(.x, "DEMO"))
  map(year, ~download_nhanes(.x, "PHTHTE"))
  map(year, ~download_nhanes(.x, "BMX"))
}
```
We created a function (`download_nhanes`) to download data in NHANES according to the year and data category. Then we used this function and `map` to download demographics data, phthalates metabolites data and body measures data from 2011 to 2016 into three local files.


## Read and clean the data
```{r}
read_file_data = function(data_category){
  path = str_c("./data/", data_category, "/")
  file_name = tibble(file_name = list.files(path))
  file_name %>% 
    mutate(map(str_c(path, file_name), ~read.xport(.x))) %>% 
    unnest() 
}

phthte = read_file_data("PHTHTE")
demo = read_file_data("DEMO")
bmx = read_file_data("BMX")

phthte_demo = inner_join(demo, phthte, by = "SEQN") 
phthte_demo_bmx = inner_join(phthte_demo, bmx, by = "SEQN")

phthte_demo_bmx =
  phthte_demo_bmx %>% 
  select(id = SEQN, year = file_name, gender = RIAGENDR, age = RIDAGEYR, race = RIDRETH3, income = INDFMPIR, 
         pregnancy_status = RIDEXPRG, bmi_cate = BMDBMIC, bmi = BMXBMI,MEP = URXMEP, MnBP = URXMBP, 
         MiBP = URXMIB, MCPP = URXMC1, MBzP = URXMZP, MEHP = URXMHP, MEHHP = URXMHH, MEOHP = URXMOH) %>%
  mutate(phthte_all = MEP + MnBP + MiBP + MCPP + MBzP + MEHP + MEHHP + MEHHP,
         race = factor(race, levels = c(1, 2, 3, 4, 6, 7), labels = c("mexican_american", "other_hispanic",
                                    "non_hispanic_white", "non_hispanic_black", "non_hispanic_asian", "other_race")),
         pregnancy_status = factor(pregnancy_status, levels = c(1, 2, 3), labels = c("yes", "no", "unknown")),
         gender = factor(gender, levels = c(1, 2), labels = c("male", "female")),
         bmi_cate = factor(bmi_cate, levels = c(1, 2, 3, 4), labels = c("underweight", "normal weight", "Overweight",
                                                                        "obese")),
         year = str_remove(year, "BMX"),
         year = str_remove(year, ".XPT")) %>%
  gather(key = "phthte", value = "concentrate", MEP:phthte_all) %>% 
  mutate(log_value = log(concentrate)) %>% 
  filter(!is.na(concentrate))

phthte_demo_bmx_1 =  phthte_demo_bmx %>% 
  filter(age %in% 2:19, phthte == "MEP") %>% 
  mutate(binomial = ifelse(bmi_cate == 3 | bmi_cate == 4, 1, 0)) %>% 
  filter(!is.na(binomial))

a = lm(log_value ~ age + income + race  + gender + gender + binomial, data = phthte_demo_bmx_1)
summary(a)

```

We created a function (`read_file_data`) to read and combine data  with one document. And we applied this function to three files and got integrated demographics data, phthalates metabolites data and body measures data from 2011 to 2016 respectively. Then we used `inner_join` to integrate three datasets by `SEQN`.

The final dataset contains ``

## Exploratory analysis

```{r}
phthte_demo_bmx %>% 
  mutate(year = ifelse(year == "2011-2012", 1, 
                       ifelse(year == "2013-2014", 2, 3))) %>% 
  group_by(year, phthte) %>% 
  summarize(mean = mean(log_value)) %>% 
  ggplot(aes(x = year, y = mean, color = factor(phthte))) +
  geom_line() +
  geom_point()

phthalate = phthte_demo_bmx %>% 
  mutate(age_cat = ifelse(age >= 2 & age <= 19, 1, 
                          ifelse(age >= 20 & age <= 39, 2, 
                                 ifelse(age >= 40 & age <= 59, 3, 
                                        ifelse(age >= 60 & age <= 79, 4, 5)))))
## effect of gender
phthalate %>% 
  filter(age_cat == 1) %>%
  ggplot(aes(x = year, y = log_value, fill = gender)) +
  geom_boxplot() +
  facet_grid(~factor(phthte))

phthalate %>% 
  filter(age_cat != 1) %>% 
  ggplot(aes(x = year, y = log_value, fill = gender)) +
  geom_boxplot() +
  facet_grid(~factor(phthte))

## effect of age
phthalate %>% 
  filter(gender == "male") %>%
  mutate(age_cat = factor(age_cat)) %>% 
  mutate(age_cat = fct_reorder(age_cat, log_value)) %>%
  ggplot(aes(x = year, y = log_value, fill = factor(age_cat))) +
  geom_boxplot() +
  facet_grid(~factor(phthte))

phthalate %>% 
  filter(gender == "female") %>%
  ggplot(aes(x = year, y = log_value, fill = factor(age_cat))) +
  geom_boxplot() +
  facet_grid(~factor(phthte))

phthalate %>% 
  ggplot(aes(x = year, y = log_value, fill = factor(age_cat))) +
  geom_boxplot() +
  facet_grid(~factor(phthte))

## effect of race
phthalate %>% 
  filter(age_cat == 1) %>%
  mutate(race = fct_reorder(race, log_value)) %>% 
  ggplot(aes(x = year, y = log_value, fill = race)) +
  geom_boxplot() +
  facet_grid(~factor(phthte))

phthalate %>% 
  filter(age_cat != 1) %>%
  mutate(race = fct_reorder(race, log_value)) %>% 
  ggplot(aes(x = year, y = log_value, fill = race)) +
  geom_boxplot() +
  facet_grid(~factor(phthte))

## effect of income
phthalate %>% 
  filter(age_cat == 1) %>%
  ggplot(aes(x = income, y = log_value, color = year)) +
  geom_smooth(se = F) +
  facet_grid(~factor(phthte))

phthalate %>% 
  filter(age_cat != 1) %>%
  ggplot(aes(x = income, y = log_value, color = year)) +
  geom_smooth(se = F) +
  facet_grid(~factor(phthte))

## effect of BMI
phthalate %>% 
  filter(age_cat != 1) %>%
  ggplot(aes(x = bmi, y = log_value, color = year)) +
  geom_smooth(se = F) +
  facet_grid(~factor(phthte))

phthalate %>% 
  filter(age_cat == 1) %>%
  filter(!is.na(bmi_cate)) %>% 
  mutate(bmi_cate = fct_reorder(bmi_cate, log_value)) %>% 
  ggplot(aes(x = year, y = log_value, fill = factor(bmi_cate))) +
  geom_boxplot() +
  facet_grid(~factor(phthte))

## effect of pregnancy status
phthalate %>% 
  filter(!is.na(pregnancy_status)) %>% 
  mutate(pregnancy_status = fct_reorder(pregnancy_status, log_value)) %>%
  ggplot(aes(x = year, y = log_value, fill = factor(pregnancy_status))) +
  geom_boxplot() +
  facet_grid(~factor(phthte))

## lm
phthalate %>% 
  filter(age_cat != 1 & phthte == "phthte_all") %>%
  lm(bmi~log_value+age+gender+race+income, data = .) %>% summary()
  


## glm for bmi and concentration
phthalate_bmi = phthalate %>% 
  filter(age_cat != 1) %>%
  mutate(overweight_obese = ifelse(bmi >= 25, 1, 0)) %>% 
  mutate(age_cat = factor(age_cat))
  
phthalate_bmi %>% 
  filter(!is.na(overweight_obese)) %>% 
  ggplot(aes(x = year, y = log_value, fill = factor(overweight_obese))) +
  geom_boxplot() +
  facet_grid(~factor(phthte))

phthalate_bmi %>% 
  filter(!is.na(overweight_obese)) %>% 
  filter(phthte == "phthte_all") %>% 
  ggplot(aes(x = year, y = log_value, fill = factor(overweight_obese))) +
  geom_boxplot() +
  facet_grid(~factor(gender))
  
phthalate_bmi %>% 
  filter(phthte == "phthte_all") %>% 
  glm(overweight_obese~log_value+age_cat+gender+race+income+gender*log_value, data = ., family = binomial()) %>% 
  summary()

phthalate_bmi %>% 
  filter(!is.na(overweight_obese)) %>% 
  filter(phthte == "phthte_all") %>%
  ggplot(aes(x = log_value, y = overweight_obese)) +
  geom_point() +
  geom_smooth() +
  facet_grid(~gender)

phthte_demo_bmx %>% 
  filter(!is.na(bmi_cate)) %>%
  filter(phthte == "phthte_all") %>%
  mutate(bmi_cat = ifelse(bmi_cate == "Overweight" | bmi_cate == "obese", 1, 0)) %>%
  ggplot(aes(x = log_value, y = bmi_cat)) +
  geom_point() +
  geom_smooth() +
  facet_grid(~gender)

phthalate %>% 
  filter(age_cat != 1) %>%
  filter(phthte == "phthte_all") %>%
  ggplot(aes(x = log_value, y = bmi)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~gender)
```


## Tendency analysis
```{r}
pd_tend = phthe_demo %>%
  group_by(year) %>%
  summarize(total = n(),
            proportion = length(which(phthe_combin == 1))/total)

pd_tend %>%
  ggplot(aes(x = year, y = proportion)) +
  geom_histogram(stat = "identity")

phthe_demo %>%
  ggplot(aes(x = year, y = phthe, fill = factor(year))) +
  geom_violin()
```

## Population compare

```{r}
phthte_by_year = phthte_demo %>% 
  select(year, gender, race, age, phthe) %>% 
  nest(gender:phthe)


gender_race_plot = function(year, gender_race_data) {
   gender_race_data %>% 
   mutate(gender = as.factor(gender),
          race = as.factor(race)) %>% 
   mutate(race = forcats::fct_reorder(race, gender_race_data$phthe)) %>% 
   ggplot(aes(x = race, y = phthe, fill = gender)) + 
     geom_boxplot() + 
     labs(title = str_c("Urine phthte level of differnet gender and race group in ", year), y = "Urine phthte level") +
     theme(axis.text.x = element_text(face = "plain", color = "black", size = 10, angle = 30,hjust = 1))
 }

gender_race_plot(phthe_by_year[[1,1]],phthe_by_year$data[[1]])

age_phthte_plot = function(year, age_data) {
  age_data %>% 
    mutate(age = cut(age,  breaks = c(0, 12, 18, 35, 55, Inf), labels = c("Young children(0-12ys)", "Teenagers(13-18ys)", "Young adults(19-35ys)", "Middle-aged adults(36-55ys)", "Older adults(>55ys)"))) %>% 
    ggplot(aes(x = age, y = phthe)) + 
    geom_boxplot(fill = "brown1") + 
    theme(axis.text.x = element_text(face = "plain", color = "black", size = 10, angle = 30,hjust = 1))
}
age_phthte_plot(phthe_by_year[[1,1]],phthe_by_year$data[[1]])

```




