---
title: "Report"
author: "Jun Lu, Yun He, Chu Yu, Chunxiao Zhai, Haoran Hu"
date: "12/2/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tableone)
library(SASxport)
library(patchwork)
library(emmeans)
library(scales)
knitr::opts_chunk$set(
    fig.align = 'center',
    fig.width = 7,
    fig.asp = 0.80,
    message = F,
    warning = F
 )
theme_set(theme_bw() + theme(legend.position = "bottom"))
```

## Motivation

Reason about topic change: Our group first wanted to work on the topic of obesity. However, the datasets we found weren't able to meet our goals. And we also found the topic not fascinating enough. Thus, we decided to switch our topic to plasticizer pollution and explore its effect on obesity as well.

Plasticizers, mainly phthalates, can interrupt the endocrine system even at low exposure levels, and there is evidence of plasticizers depositing in animal brains. Concerns have been rising in pediatricians and scientists. Obesity, which is a major public health problem across the world, is also associated with plasticizer exposure. Fat at first and now sugar have been blamed for causing obesity, while increasing evidence shows that plasticizer pollution is also playing an important role. However, effects of plasticizers on bodyweight within different age and gender groups are different. With more detailed monitoring data on plasticizer exposure available at NHANES datasets, we can now explore the relationship between body weight and plasticizer exposure.

## Related works
* Papers:

1. [Phthalates and Their Alternatives: Health and Environmental Concerns] [1]11
2. [Gender- and Age-Specific Relationships Between Phthalate Exposures and Obesity in Shanghai Adults] [2]
3. [Developmental Effects of Endocrine-disrupting Chemicals in Wildlife and Humans] [3]
4. [DI-2-Ethylhexyl Phthalate and Endocrine Disruption: A Review] [4]
5. [Phthalates Impact Human Health: Epidemiological Evidences and Plausible Mechanism of Action] [5]
6. [Phthalate Exposure and Childhood Obesity] [6]
7. [Endocrine Disruptors and Obesity] [7]

[1]: <http://ec.europa.eu/environment/aarhus/pdf/35/Annex_11_report_from_Lowell_Center.pdf>
[2]: <https://doi.org/10.1007/s00244-017-0441-6>
[3]: <https://doi.org/10.1289/ehp.93101378>
[4]: <https://doi.org/10.2174/1568008043340017>
[5]: <https://doi.org/10.1016/j.jhazmat.2017.06.036>
[6]: <https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4114051/>
[7]: <https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5359373/>

* Websites:

1. [Plasticisers Information Center] [8]
2. [Global Health Observatory (GHO) Data] [9]
3. [Definition; epidemiology; and etiology of obesity in children and adolescents] [10]
4. [Bisphenol A (BPA): Use in Food Contact Application] [11]
5. [Endocrine Disruptors] [12]

[8]: <https://www.plasticisers.org>
[9]: <https://www.who.int/gho/ncd/risk_factors/overweight/en/>
[10]: <https://www.uptodate.com/contents/definition-epidemiology-and-etiology-of-obesity-in-children-and-adolescents>
[11]: <https://www.fda.gov/newsevents/publichealthfocus/ucm064437.htm>
[12]: <https://www.niehs.nih.gov/health/topics/agents/endocrine/index.cfm>

## Initial questions: 
* Are people exposed at the same level? Who has been exposed most?
* Are distributions of different types of plasticizers same in different populations?
* Are people exposed at the same levels of plasticizers affected the same way? 
* Is there a dose response relationship? Is this relationship linear?

## Data sources
All data were retrieved from the the [National Health and Nutrition Examination Survey](https://www.cdc.gov/nchs/nhanes/index.htm). The National Health and Nutrition Examination Survey (NHANES) is a program of studies designed to assess the health and nutritional status of adults and children in the United States. 

We downloaded demographics data ([DEMO2011-2012][13], [DEMO2013-2014][14] and [DEMO2015-2016][15]), phthalates metabolites data ([PHTHTE2011-2012][16], [PHTHTE2013-2014][17] and [PHTHTE2015-2016][18]) and body measures data ([BMX2011-2012][19], [BMX2013-2014][20] and [BMX2015-2016][21]) into three local files.

[13]:https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/DEMO_G.XPT
[14]:https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/DEMO_H.XPT
[15]:https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/DEMO_I.XPT
[16]:https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/PHTHTE_G.XPT
[17]:https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/PHTHTE_H.XPT
[18]:https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/PHTHTE_I.XPT
[19]:https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/BMX_G.XPT
[20]:https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/BMX_H.XPT
[21]:https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/BMX_I.XPT


Variables selected from the demographics dataset:

* `SEQN `: Respondent sequence number
* `RIAGENDR`: Gender
* `RIDAGEYR`: Age
* `RIDRETH3`: Race and Hispanic origin information, with Non-Hispanic Asian Category
* `INDFMPIR`: Ratio of family income to poverty

Variables selected from the phthalates metabolites dataset:

* `SEQN `: Respondent sequence number
* `URXMEP`: Mono-ethyl phthalate (ng/mL)
* `URXMBP`: Mono-n-butyl phthalate (ng/mL)
* `URXMIB`: Mono-isobutyl phthalate (ng/mL)
* `URXMC1`: Mono-(3-carboxypropyl) phthalate (ng/mL)
* `URXMZP`: Mono-benzyl phthalate (ng/mL)
* `URXMHP`: Mono-(2-ethyl)-hexyl phthalate (ng/mL)
* `URXMHH`: Mono-(2-ethyl-5-hydroxyhexyl) phthalate (ng/mL)
* `URXMOH`: Mono-(2-ethyl-5-oxohexyl) phthalate (ng/mL)

Variables selected from the body measures dataset:

* `SEQN `: Respondent sequence number
* `BMXBMI`: Body Mass Index (kg/m^2)
* `BMDBMIC`: BMI Category - Children/Youth

## Get the data

```{r}
download_nhanes = function(year, data_category){
  letter = c("2011-2012" = "G", "2013-2014" = "H", "2015-2016" = "I")
  url = str_c("https://wwwn.cdc.gov/Nchs/Nhanes/", year, "/", data_category, "_", letter[year], ".XPT")
  destfile_name = str_c("./data/", data_category, "/", data_category, year, ".XPT")
  download.file(url, destfile = destfile_name, method = "curl")
}


if (!file.exists("data")) {
  dir.create("./data")
  dir.create("./data/DEMO")
  dir.create("./data/PHTHTE")
  dir.create("./data/BMX")
  year = c("2011-2012", "2013-2014", "2015-2016")
  map(year, ~download_nhanes(.x, "DEMO"))
  map(year, ~download_nhanes(.x, "PHTHTE"))
  map(year, ~download_nhanes(.x, "BMX"))
}
```

We created a function (`download_nhanes`) to download NHANES data from three different survey years, which are '2011-2012', '2013-2014' and '2015-2016'. And we downloaded data on demographics, body measures and phthalates metabolites using this function and `map` into three local files.

## Read and clean the data

```{r}
read_file_data = function(data_category){
  path = str_c("./data/", data_category, "/")
  file_name = tibble(file_name = list.files(path))
  file_name %>% 
    mutate(map(str_c(path, file_name), ~read.xport(.x))) %>% 
    unnest() 
}

phthte = read_file_data("PHTHTE")
demo = read_file_data("DEMO")
bmx = read_file_data("BMX")

phthte_demo = inner_join(demo, phthte, by = "SEQN") 
phthte_demo_bmx = inner_join(phthte_demo, bmx, by = "SEQN")

phthte_demo_bmx =
  phthte_demo_bmx %>% 
  select(id = SEQN, gender = RIAGENDR, age = RIDAGEYR, race = RIDRETH3, income = INDFMPIR, 
         bmi_cat = BMDBMIC, bmi = BMXBMI,MEP = URXMEP, MnBP = URXMBP, MiBP = URXMIB, 
         MCPP = URXMC1, MBzP = URXMZP, MEHP = URXMHP, MEHHP = URXMHH, MEOHP = URXMOH) %>%
  mutate(phthalate_all = MEP + MnBP + MiBP + MCPP + MBzP + MEHP + MEHHP + MEHHP,
         race = factor(race, levels = c(1, 2, 3, 4, 6, 7), 
                       labels = c("mexican_american", "other_hispanic", "non_hispanic_white",
                                  "non_hispanic_black", "non_hispanic_asian", "other_race")),
         gender = factor(gender, levels = c(1, 2), labels = c("male", "female")),
         bmi_cat = factor(bmi_cat, levels = c(1, 2, 3, 4), 
                          labels = c("underweight", "normal weight", "Overweight","obese")),
         age_cat = ifelse(age >= 2 & age <= 19, 1, 2),
         age_cat = factor(age_cat, levels = c(1, 2), 
                          labels = c("children", "adults")),
         poverty_status = ifelse(income >= 1, 2, 1), 
         poverty_status = factor(poverty_status, levels = c(1, 2), 
                                 labels = c("poverty", "nonpoverty"))) %>%
  filter(!is.na(phthalate_all)) %>% 
  gather(key = "phthalate", value = "concentrate", MEP:phthalate_all) %>% 
  mutate(log_value = log(concentrate)) %>% 
  select(-income)

str(phthte_demo_bmx)
```

We created a function (`read_file_data`) to read and combine datasets within one file. And we applied this function to each file where we had the NHANES data downloaded and finally got three datasets with integrated demographics data, phthalates metabolites data and body measures data ranging from 2011 to 2016, respectively. Then we used `inner_join` to integrate these three datasets by `SEQN`.

We selected variables of interest, and converted `gender`, `race`, `bmi_cat` and `poverty_status` into factors. For each individual, total exposure (`phthte_all`) was calculated by adding the exposure of all eight phthalates metabolites. Then we used `gather` to aggregate data. We also took the log transformation on `concentrate` to create `log_value`. 

The final dataset contains data on 8 urinary phthalate metabolites and related information from 8149 participants in the National Health and Nutrition Examination Survey (NHANES) 2011–2016. It contains `r nrow(phthte_demo_bmx)` observations and `r ncol(phthte_demo_bmx)` variables.

* `id`: Respondent sequence number
* `gender`: Gender
* `race`: Race and Hispanic origin information, with Non-Hispanic Asian Category
* `poverty_status`: Poverty or nonpoverty
* `bmi`: Body mass index (kg/m**2)
* `bmi_cat`: BMI Category (only for children/youth)
* `age_cat`: Child or adult
* `phthalate`: Type of phthalate
* `concentrate`: Concentration of the components
* `log_value`: log value of the concentration

## Exploratory analysis

### Summary statistics for demographics data

```{r}
phthte_demo_bmx %>% 
  filter(phthalate == "phthalate_all") %>% 
  CreateTableOne(data = ., 
                 vars = c("gender", "race", "age_cat", "poverty_status", "age", "bmi")) %>% 
  print(printToggle = FALSE, noSpaces = TRUE, showAllLevels = TRUE) %>% 
  knitr::kable()
```

### Summary statistics for phthalates metabolites data

```{r}
phthte_demo_bmx %>% 
  select(-log_value) %>% 
  spread(key = "phthalate", value = "concentrate") %>% 
  CreateTableOne(data = ., 
                 vars = c("MBzP", "MCPP", "MEHHP", "MEHP", "MEOHP", "MEP", 
                          "MiBP", "MnBP", "phthalate_all" )) %>% 
  print(printToggle = FALSE, noSpaces = TRUE, smd = TRUE) %>% 
  knitr::kable()
```

We computed a few summary statistics and checked whether there are enough samples to do analyses in each subgroup (race, gender, age and poverty status).

## Percent contribution of individual phthalates to the sum-total exposure

```{r}
bar_1 = 
  phthte_demo_bmx %>% 
  filter(phthalate != "phthalate_all") %>% 
  mutate(race = factor(race, levels = c("mexican_american", "other_hispanic", "non_hispanic_white", "non_hispanic_black", "non_hispanic_asian", "other_race"), labels = c("Mexican American", "Other Hispanic", "Non Hispanic White", "Non Hispanic Black", "Non Hispanic Asian", "Other race"))) %>% 
  group_by(race, phthalate) %>% 
  summarize(mean = mean(concentrate)) %>% 
  ggplot(aes(x = race, y = mean, fill = phthalate)) + 
  geom_bar(position = "fill",stat = "identity", width = 0.4) +
  scale_y_continuous(labels = percent_format()) +
  theme(axis.text.x = element_text(angle = 10, hjust = 1)) +
  scale_fill_brewer(palette = "Pastel2") +
  labs(
    title = "Percent contribution of each type of phthalates to the sum-total phthalates exposure",
    x = "Race",
    y = "Percent contribution"
  )

bar_2 = 
  phthte_demo_bmx %>% 
  filter(phthalate != "phthalate_all") %>% 
  filter(!is.na(poverty_status)) %>% 
  group_by(poverty_status, phthalate) %>% 
  summarize(mean = mean(concentrate)) %>% 
  ggplot(aes(x = poverty_status, y = mean, fill = phthalate)) + 
  geom_bar(position = "fill",stat = "identity", width = 0.4) +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_brewer(palette = "Pastel2") +
  labs(
    x = "Poverty status",
    y = "Percent contribution"
  ) +
    guides(fill = FALSE)

bar_3 =
  phthte_demo_bmx %>% 
  filter(phthalate != "phthalate_all") %>% 
  group_by(age_cat, phthalate) %>% 
  summarize(mean = mean(concentrate)) %>% 
  ggplot(aes(x = age_cat, y = mean, fill = phthalate)) + 
  geom_bar(position = "fill",stat = "identity", width = 0.4) +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_brewer(palette = "Pastel2") +
  labs(
    x = "Age status",
    y = NULL
  ) +
    guides(fill = FALSE)

bar_4 = 
  phthte_demo_bmx %>% 
  filter(phthalate != "phthalate_all") %>% 
  group_by(gender, phthalate) %>% 
  summarize(mean = mean(concentrate)) %>% 
  ggplot(aes(x = gender, y = mean, fill = phthalate)) + 
  geom_bar(position = "fill",stat = "identity", width = 0.4) +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_brewer(palette = "Pastel2") +
  labs(
    x = "Gender",
    y = NULL
  ) +
  guides(fill = FALSE)

bar_1 + (bar_2 + bar_3 + bar_4) + plot_layout(ncol = 1)
```

We made barplots to show percent contribution of each phthalate metabolite to the sum-total exposure among different subgroups. We found that mono-ethyl phthalate (MEP) contributed most to the sum-total exposure. And percent contribution patterns are different among different gender and age groups.

## Density plots of the sum-total exposure

```{r}
p1_density = 
  phthte_demo_bmx %>% 
  filter(phthalate == "phthalate_all") %>% 
  ggplot(aes(x = concentrate)) + 
  geom_density(fill = "orange", alpha = 0.5) +
  labs(
    title = "Density plot of the sum-total exposure",
    y = "Density",
    x = "The sum-total exposure (ng/mL))"
  )

p2_density =
  phthte_demo_bmx %>% 
  filter(phthalate == "phthalate_all") %>% 
  ggplot(aes(x = log_value)) + 
  geom_density(fill = "orange", alpha = 0.5) +
  labs(
    title = "Density plot of log(the sum-total exposure)",
    y = "Density",
    x = "Log(sum-total exposure)"
  )

p1_density + p2_density + plot_layout(ncol = 1)
```

As the distribution of the sum-total phthalate exposure is extremely right skewed, we used log(sum-total exposure) (`log_value`) to do subsequent analyses.

## Violin plots of log(sum-total exposure)

```{r}
race_dist =
  phthte_demo_bmx %>% 
  filter(phthalate == "phthalate_all") %>% 
  mutate(race = forcats::fct_reorder(race, log_value, .desc = T)) %>% 
  ggplot(aes(x = race, y = log_value, fill = race)) +
  geom_violin() +
  stat_summary(fun.y = median, geom = "point", size = 1) +
  labs(
    x = "Race",
    y = "Log(sum-total exposure)",
    title = "Distribution of log(total exporsure) in different races"
    ) +
  theme(axis.text.x = element_text(angle = 10, hjust = 1)) +
  scale_fill_brewer(palette = "Pastel2")

age_dist =
  phthte_demo_bmx %>% 
  filter(phthalate == "phthalate_all") %>% 
  mutate(age_cat = forcats::fct_reorder(age_cat, log_value, .desc = T)) %>% 
  ggplot(aes(x = age_cat, y = log_value, fill = age_cat)) +
  geom_violin() +
  stat_summary(fun.y = median, geom = "point", size = 1) +
  labs(
    x = "Age status",
    y = NULL
    ) +
  guides(fill = guide_legend(title = NULL)) +
  scale_fill_brewer(palette = "Pastel2") 

poverty_status_dist =
  phthte_demo_bmx %>% 
  filter(phthalate == "phthalate_all") %>% 
  filter(!is.na(poverty_status)) %>% 
  mutate(poverty_status = forcats::fct_reorder(poverty_status, log_value, .desc = T)) %>% 
  ggplot(aes(x = poverty_status, y = log_value, fill = poverty_status)) +
  geom_violin() +
  stat_summary(fun.y = median, geom = "point", size = 1) +
  labs(
    x = "Poverty_status",
    y = "Log(sum-total exposure)",
    title = "Distribution of log(total exporsure) in different subpopulations"
    ) +
  guides(fill = guide_legend(title = NULL)) +
  scale_fill_brewer(palette = "Pastel2")
  

gender_dist =
  phthte_demo_bmx %>% 
  filter(phthalate == "phthalate_all") %>% 
  mutate(gender = forcats::fct_reorder(gender, log_value, .desc = T)) %>% 
  ggplot(aes(x = gender, y = log_value, fill = gender)) +
  geom_violin() +
  stat_summary(fun.y = median, geom = "point", size = 1) +
  labs(
    x = "Gender",
    y = NULL
    ) +
  guides(fill = guide_legend(title = NULL)) +
  scale_fill_brewer(palette = "Pastel2") 
  

poverty_status_dist + gender_dist + age_dist + plot_layout(nrow = 1)
race_dist
```

We stratified the study population on the basis of gender, poverty status, race and age, and made violin plots for each subgroup. From violin plots, we found that there were between-group differences in log(sum-total exposure) on the basis of race and poverty status. However, differences are not very obvious in violin plots.

## LS means analysis

In order to compare log(sum-total exposure) value in different subgroups, we fitted a multilinear model and calculated least square means.

### Fit a  multilinear model

```{r}
multi_fit = 
  phthte_demo_bmx %>% 
  filter(phthalate == "phthalate_all") %>%
  lm(log_value ~ age + gender + race + poverty_status + bmi , data = .)

summary(multi_fit)
```

We fitted a multilinear model (log_value ~ age + gender + race + poverty_status + bmi) and found that gender, race, poverty_status and bmi are significant predictors in this model. And then we used this model to calculate least square means.

### Compare least square means

```{r}
race_ls = lsmeans(multi_fit, pairwise ~ race, adjust = "tukey")

p1_race =
  race_ls$lsmeans %>%
  broom::tidy() %>% 
  mutate(race = forcats::fct_reorder(race, estimate, .desc = T)) %>% 
  ggplot(aes(x = race, y = estimate)) + 
  geom_errorbar(aes(x = race, ymin = conf.low, ymax = conf.high), size = 1, width = 0.2) +
  geom_point(color = "orange", size = 2) +
  labs(
    title = "LS means of log(total exposure) among different subpopulations",
    x = "Race",
    y = "LS means of log(total exposure)"
  ) +
  theme(axis.text.x = element_text(angle = 10, hjust = 1))

poverty_ls = lsmeans(multi_fit, pairwise ~ poverty_status, adjust = "tukey")
p2_poverty =
  poverty_ls$lsmeans %>%
  broom::tidy() %>% 
  mutate(poverty_status = forcats::fct_reorder(poverty_status, estimate, .desc = T)) %>% 
  ggplot(aes(x = poverty_status, y = estimate)) + 
  geom_errorbar(aes(x = poverty_status, ymin = conf.low, ymax = conf.high), size = 1, width = 0.1) +
  geom_point(color = "orange", size = 2) +
  labs(
    x = "Poverty status",
    y = "LS means of log(total exposure)"
  ) 

gender_ls = lsmeans(multi_fit, pairwise ~ gender, adjust = "tukey")
p3_gender =
  gender_ls$lsmeans %>%
  broom::tidy() %>% 
  mutate(gender = forcats::fct_reorder(gender, estimate, .desc = T)) %>% 
  ggplot(aes(x = gender, y = estimate)) + 
  geom_errorbar(aes(x = gender, ymin = conf.low, ymax = conf.high), size = 1, width = 0.1) +
  geom_point(color = "orange", size = 2) +
  labs(
    x = "Gender",
    y = NULL
  ) 


p1_race + (p2_poverty + p3_gender) + plot_layout(ncol = 1)
```

Plots above show least square means and 95% confidence intervals of log(sum-total exposure) by race, poverty status and gender. (Least square means are means for groups that are adjusted for other terms in the model)

* Compared to other race groups, levels of the sum-total exposure were significantly higher in non_hispanic_blacks.
* Compared to the group who are living in nonpoverty, levels of the sum-total exposure were significantly higher in the group who are living in poverty.
* Compared to females, levels of the sum-total exposure were higher in males.

## Obesity analysis

In this part, we tried to explore the association of the sum-total phthalate exposure and the body mass index (BMI) and obesity outcome.

### Explore the association between the phthalate exposure and obesity status

```{r}
phthte_children = phthte_demo_bmx %>% filter(age_cat == "children")

phthte_adult = phthte_demo_bmx %>% 
  filter(age_cat == "adults") %>%
  mutate(overweight_status = ifelse(bmi >= 25, 1, 2),
         overweight_status = factor(overweight_status, levels = c(1, 2), labels = c("overweight", "normal"))) %>% 
  select(-bmi_cat)

phth_obese_children = phthte_children %>%
  filter(phthalate == "phthalate_all") %>%
  ggplot(aes(x = log_value, y = bmi)) +
  geom_point(aes(color = gender), alpha = 0.5) +
  geom_smooth(method = "lm") +
  facet_grid(~gender) +
  labs(
    x = "Log(sum-total exposure)",
    y = "Body mass index (BMI)",
    title = "Association between the phthalate exposure and obesity status among children"
  ) +
  scale_color_brewer(palette = "Pastel2")

phth_obese_adult = phthte_adult %>%
  filter(phthalate == "phthalate_all") %>%
  ggplot(aes(x = log_value, y = bmi)) +
  geom_point(aes(color = gender), alpha = 0.5) +
  geom_smooth(method = "lm") +
  facet_grid(~gender) +
  labs(
    x = "Log(sum-total exposure)",
    y = "Body mass index (BMI)",
    title = "Association between the phthalate exposure and obesity status among adults"
  ) +
  scale_color_brewer(palette = "Pastel2")

phth_obese_children/phth_obese_adult
```

Plots above show a positive association of phthalate and BMI among both children and adults. Among children, the association tends to be stronger in males than that in females. However, among adults, the association tends to be stronger in females than that in males. 

### Fit the GLM model

```{r}
## fit the model in children
### male
boy_mod = phthte_children %>% 
  filter(phthalate == "phthalate_all",
         gender == "male") %>%
  mutate(bmi_cat = ifelse(bmi_cat %in% c("Overweight", "obese"), 1, 0)) %>%  
  glm(bmi_cat~log_value+age+race+poverty_status, data = ., family = binomial()) 

boy_est = broom::tidy(boy_mod) %>% 
  mutate(OR = exp(estimate)) 
boy_conf = broom::confint_tidy(boy_mod) %>% 
  mutate(conf_low = exp(conf.low),
         conf_high = exp(conf.high))
boy_OR = bind_cols(boy_est, boy_conf) %>% 
  filter(term == "log_value") %>% 
  mutate(gender = "male",
         group = "children") %>% 
  select(group, gender, OR, conf_low, conf_high)

### female
girl_mod = phthte_children %>% 
  filter(phthalate == "phthalate_all",
         gender == "female") %>%
  mutate(bmi_cat = ifelse(bmi_cat %in% c("Overweight", "obese"), 1, 0)) %>%  
  glm(bmi_cat~log_value+age+race+poverty_status, data = ., family = binomial()) 

girl_est = broom::tidy(girl_mod) %>% 
  mutate(OR = exp(estimate)) 
girl_conf = broom::confint_tidy(girl_mod) %>% 
  mutate(conf_low = exp(conf.low),
         conf_high = exp(conf.high))
girl_OR = bind_cols(girl_est, girl_conf) %>% 
  filter(term == "log_value") %>% 
  mutate(gender = "female",
         group = "children") %>% 
  select(group, gender, OR, conf_low, conf_high)


## fit the model in adults
### male
male_mod = phthte_adult %>% 
  filter(phthalate == "phthalate_all",
         gender == "male") %>%
  mutate(overweight_status = ifelse(overweight_status == "overweight", 1, 0)) %>%  
  glm(overweight_status~log_value+age+race+poverty_status, data = ., family = binomial())

male_est = broom::tidy(male_mod) %>% 
  mutate(OR = exp(estimate)) 
male_conf = broom::confint_tidy(male_mod) %>% 
  mutate(conf_low = exp(conf.low),
         conf_high = exp(conf.high))
male_OR = bind_cols(male_est, male_conf) %>% 
  filter(term == "log_value") %>% 
  mutate(gender = "male",
         group = "adult") %>% 
  select(group, gender, OR, conf_low, conf_high)

### female
female_mod = phthte_adult %>% 
  filter(phthalate == "phthalate_all",
         gender == "female") %>%
  mutate(overweight_status = ifelse(overweight_status == "overweight", 1, 0)) %>%  
  glm(overweight_status~log_value+age+race+poverty_status, data = ., family = binomial()) 
female_est = broom::tidy(female_mod) %>% 
  mutate(OR = exp(estimate)) 
female_conf = broom::confint_tidy(female_mod) %>% 
  mutate(conf_low = exp(conf.low),
         conf_high = exp(conf.high))
female_OR = bind_cols(female_est, female_conf) %>% 
  filter(term == "log_value") %>% 
  mutate(gender = "female",
         group = "adult") %>% 
  select(group, gender, OR, conf_low, conf_high)

bind_rows(boy_OR, girl_OR, male_OR, female_OR) %>% 
  mutate(
    OR = round(OR, digits = 2),
    conf_low = round(conf_low, digits = 2),
    conf_high = round(conf_high, digits = 2),
    OR = paste0(OR, "(", conf_low, ", ", conf_high, ")"))  %>% 
  select(group, gender, OR) %>% 
  spread(gender, OR) %>% 
  knitr::kable()
```

The table above summarizes the change in odds of being overweight/obese due to increase in the magnitude of sum-total phthalate exposure, after adjusting for age, race and poverty status in the regression model. We reported the results stratified by gender, as the association between phthalate and obesity might be modified by gender. 

Among adults, for a one-unit increase in the sum-total phthalate exposure, we expect to see about 18% and 11% increase in the odds of being overweight/obese for females and males, respectively, adjusting for age, race and poverty status. 

Among children, there is no association between phthalate and obesity in females statistically. While in males, for a one-unit increase in the sum-total phthalate exposure, we expect to see about 15% increase in the odds of being overweight/obese, adjusting for age, race and poverty status. 

### Discussion: 
* What were your findings? Are they what you expect? 
We were expecting the plasticizers influence male population more for their lower baseline estrogen levels, but we found adult women are more influenced than men, and only male children are influenced.
* What insights into the data can you make?

* The obesity pandemic:
Cardio-cerebralvascular diseases have become the leading cause of death worldwide (with ischemic heart disease ranked No.1 and stroke ranked No.3 in 2017), in which diabetes and obesity are the top risk factors along with tobacco use. Disability and early death due to obesity and overweight have increased by 28.9% in the US from 1990 to 2016. In the mean time, obesity and overweight rate have been rapidly increasing in developing countries. Globally, in 2016, 39% of women and 39% of men aged 18 and over were overweight.

* The increasing plasticizer evidence:
Is this health crisis fully due to the diet? First fat and now sugar have been blamed for causing obesity but increasing evidence have been found that pollution is playing an important role. Plasticizers or mainly phthalates have been found to interrupt endocrine system at very low level of exposure, concerns have been rising in pediatricians and scientists. However, suspected act like estrogen agonist in human body, conclusions of how plasticizers affect bodyweight in populations of different age and genders do not always agree. With latest evidence of plasticizers depositing in human brain and more detailed exposure monitoring data of plasticizer exposure, we want to explore the relationship between body weight and plasticizer exposure in the latest NHANES datasets.

